---
title: "p8105_hw1_jc6452"
output: github_document
---

```{r library,echo = FALSE, message = FALSE}
library(palmerpenguins)
library(tidyverse)
```
# Problem 1

## importing data
```{r import}
data("penguins", package = "palmerpenguins")
summary(penguins)
nrow(penguins)
ncol(penguins)
print(mean(penguins$flipper_length_mm, na.rm = TRUE))
```
## description of *penguins* dataset

The *penguins* dataset includes the following 8 variables, species,island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, and year. Some of the notable values of the variables include is that the earliest year listed is 2007 and mean values for bill_length_mm, bill_depth_mm and flipper_length_mm is 43.92, 17.15, 200.9, respectively. The penguins in this data set weigh an average of 4202g (4.202kg). The data set size is (344 x 8), which means in contains 344 rows and 8 columns total. The mean flipper length is 200.9152, after removing the NA entries. 

## creating penguins scatterplot
```{r scatterplot}
ggplot(data = penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave('penguins_flipper_blil_plot.png')
```

# Problem 2

## creating tibble

```{r tibble}
df = 
  tibble(
  x = rnorm(10),
  vector_logical = c(x>0),
  vector_character = c("this", "is", "P8105", "data", "science", "data", "wrangling", "homework", "one", "problem"),
  vector_factor = c("low", "high", "high", "medium", "medium", "low", "high", "high", "low", "medium")
)
sample = pull(df, x)
pull_VL = pull (df, vector_logical)
pull_VC = pull(df, vector_character)
pull_VF = pull(df, vector_factor)

mean(sample)
mean(pull_VL)
mean(pull_VC)
mean(pull_VF)
```

The character vector and factor vector cannot be computed by the mean function.

## numeric logical, character and factor vector
```{r numeric, eval = FALSE }
numeric_vl = as.numeric(pull_VL)
numeric_vc = as.numeric(pull_VC)
numeric_vf = as.numeric(pull_VF)

mean(numeric_vl)
mean(numeric_vc)
mean(numeric_vf)
```

According to the warning message, "NAs introduced by coercion" for both   `numeric_vc` and `numeric_vf`. Both the character vector and factor vector, which has been applied with `as.numeric` function, outputted NA when I tried to compute the mean. This is because these are string type variables where the values inside the variable are string, a descriptive, and non-numerical type variable. Unlike the two, logical vector outputted mean of 0.5 as logical vector is boolean, hence its output can be computed in numerical term (0 when FALSE and 1 when TRUE). When viewing the `mean` function, there are methods for numeric/logical vectors, and date, date-time and time interval objects. Therefore, character and factor vectors cannot be computed while logical vectors can be. 