---
title: "p8105_hw1_jc6452"
output: github_document
---

```{r,echo = FALSE, message = FALSE}
library(palmerpenguins)
library(tidyverse)
```
# Problem 1

## importing data
```{r}
data("penguins", package = "palmerpenguins")
summary(penguins)
nrow(penguins)
ncol(penguins)
print(mean(penguins$flipper_length_mm, na.rm = TRUE))
```
## description of *penguins* dataset

The *penguins* dataset includes the following 8 variables, species,island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, and year. Some of the notable values of the variables include is that the earliest year listed is 2007 and mean values for bill_length, bill_depth and flipper_length is 43.92, 17.15, 200.9, respectively. The penguins in this dataset weigh an average of 4202g (4.202kg). The dataset size is (344 x 8), which means in contains 8 columns and 344 rows total. The mean flipper length is 200.9152, after removing the NA entries. 

## creating penguins scatterplot
```{r scatterplot}
ggplot(data = penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave('penguins_flipper_blil_plot.png')
```

# Problem 2

## creating tibble

```{r}
df = 
  tibble(
  x = rnorm(10),
  vector_logical = c(x>0),
  vector_character = c("this", "is", "P8105", "data", "science", "data", "wrangling", "homework", "one", "problem"),
  vector_factor = c("low", "high", "high", "medium", "medium", "low", "high", "high", "low", "medium")
)
sample = pull(df, x)
pull_VL = pull (df, vector_logical)
pull_VC = pull(df, vector_character)
pull_VF = pull(df, vector_factor)

mean(sample)
mean(pull_VL)
mean(pull_VC)
mean(pull_VF)
```

The character vector and factor vector cannot be computed by the mean function.

##numeric character vector and factor vector
```{r}
numeric_vc = as.numeric(pull_VC)
numeric_vf = as.numeric(pull_VF)

mean(numeric_vc)
mean(numeric_vf)
```

According to the warning message, "NAs introduced by coercion", and both the character vector and factor vector, which has been applied with `as.numeric` function, outputted NA when I tried to compute the mean. This is because these are string type variables where the values inside the variable `vc` are string and as they are descriptive, qualitative, and non-numerical. When viewing the `mean` function, there are methods for numeric/logical vectors, and date, date-time and time interval objects. Therefore, character and factor vectors cannot be computed. 